Calibration tests beyond classification

### 2021-03-15 paper/main.tex
Add missing parenthesis
Fix grammar
Use updated experimental results in the paper

\begin{figure}[!htb]
    \centering
    \begin{subfigure}[t]{0.62\textwidth}
        \centering
        \textbf{a}
        \includegraphics[valign=t,scale=0.23]{figures/ols/heatmap.pdf}
    \end{subfigure}%
    \hfill%
    \begin{subfigure}[t]{0.38\textwidth}
        \centering
        \textbf{b}
        \includegraphics[valign=t,scale=0.23]{figures/ols/quantiles.pdf}
    \end{subfigure}
    \caption{Illustration of a conditional distribution $\Prob(Y|X)$ with scalar
    feature and target. We consider a Gaussian predictive model $P$, obtained by
    ordinary least squares regression with 100 training data points (orange dots).
    Empirically the predicted quantiles on 50 validation data points appear close
    to being calibrated, although model $P$ is uncalibrated according to
    \cref{def:calibration}. Using the framework in this
    paper, on the same validation data a statistical test allows us to reject
    the null hypothesis that model $P$ is calibrated at a significance level of
    $\alpha = 0.05$ ($p < 0.025$). See~\cref{app:ols} for details.}%
    \label{fig:ols_motivation}
    %\vspace{-0.5\baselineskip}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[scale=0.35]{figures/synthetic/tests_d=10.pdf}
    \caption{Empirical test errors for 500 data sets of $n \in \{4, 16, 64, 256, 1024\}$
    samples from models with targets of dimension $d = 10$. The dashed black line
    indicates the set signficance level $\alpha = 0.05$.}%
    \label{fig:synthetic_tests_10_main}
    \vspace{-\baselineskip}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[scale=0.07]{figures/friedman/statsplot_zoom.png}
    \caption{Mean squared error (MSE), average negative log-likelihood (NLL),
    $\widehat{\mathrm{SKCE}}_k$ (SKCE), and $p$-value approximation ($p$-value) of
    ten Gaussian predictive models for the Friedman~1 regression problem versus
    the number of training iterations.
    Evaluations on the training data set (100 samples) and the test data set
    (50 samples) are displayed in green and orange, respectively. The solid line
    and its surrounding band represent the mean and the range of the 10\% to 90\%
    quantile of the evaluations of the ten models, respectively. The dashed line visualizes the
    evaluations of the ensemble models.}%
    \label{fig:friedman1_zoom}
    \vspace{-\baselineskip}
\end{figure}

@@

A validation data set of $n = 50$ i.i.d.\ pairs of $X$ and $Y$ is used to
evaluate the empirical frequency
\begin{equation*}
    n^{-1} \sum_{i=1}^n \mathbbm{1}_{[0,\tau]}\big(P(Y \leq Y_i | X = X_i)\big)
\end{equation*}
of model $P$ for quantile levels $\tau \in [0, 1]$. Model $P$ would be quantile
calibrated~\citep{Song2019}
\begin{equation*}
    \tau = \Prob_{X',Y'}\big(P(Y \leq Y' | X = X') \leq \tau \big)
\end{equation*}
for all $\tau \in [0,1]$, where $(X, Y)$ and $(X', Y')$ are independent identically
distributed pairs of random variables (see~\cref{fig:ols_quantiles}).

\begin{figure}[hpt]
    \begin{center}
        \includegraphics[scale=0.35]{figures/ols/quantiles.pdf}
        \caption{Empirical frequency versus predicted quantile for the linear regression
        model on the validation data (orange curve). The green curve indicates the theoretical ideal
        for a quantile-calibrated model.}
        \label{fig:ols_quantiles}
    \end{center}
\end{figure}

Additionally, we compute a $p$-value estimate of the null hypothesis $H_0$ that model $P$
is calibrated using an estimation of the quantile of the asymptotic distribution
of $n \widehat{\mathrm{SKCE}}_{k,n}$ with 100000 bootstrap samples
on the validation data set (see~\cref{remark:skceb_quadratic}). Kernel $k$ is chosen
as a tensor product kernel of two Gaussian kernels
\begin{equation*}
    \begin{split}
        k\big((p, y), (p', y')\big) &= \exp{\big(-W_2(p, p')\big)} \exp{\big(-(y - y')^2 \big)} \\
        &= \exp{\big(-\sqrt{(m_p - m_{p'})^2 - (\sigma_p - \sigma_{p'})^2}\big)} \exp{\big(- (y - y')^2\big)},
    \end{split}
\end{equation*}
where $W_2$ is the 2-Wasserstein distance and $m_p, m_{p'}$ and $\sigma_p, \sigma_{p'}$ denote
the mean and the standard deviation of the normal distributions $p$ and $p'$ (see~\cref{app:normal}).
We obtain $p < 0.025$ in our experiment, and hence the calibration test rejects $H_0$ at the
significance level $\alpha = 0.05$.

@@

We perform an evaluation of the convergence and computation time of the biased estimator
$\widehat{\mathrm{SKCE}}_k$ and the unbiased estimator $\widehat{\mathrm{SKCE}}_{k,B}$ with
blocks of size $B \in \{2, \sqrt{n}, n\}$. We use a tensor product kernel
\begin{equation*}
\begin{split}
    k\big((p, y), (p', y')\big) &= \exp{\big(- W_2(p, p')\big)} \exp{\big(-(y - y')^2\big)} \\
    &= \exp{\bigg(-\sqrt{(m_p - m_{p'})^2 - (\sigma_p - \sigma_{p'})^2}\bigg)} \exp{\big( - (y - y')^2\big)},
\end{split}
\end{equation*}
where $W_2$ is the 2-Wasserstein distance and $m_p, m_{p'}$ and $\sigma_p, \sigma_{p'}$
denote the mean and the standard deviation of the normal distributions $p$ and $p'$.

\Cref{fig:synthetic_error_calibrated_1,fig:synthetic_error_calibrated_10,fig:synthetic_error_uncalibrated_1,fig:synthetic_error_uncalibrated_10} visualize the mean absolute error and the variance
of the resulting estimates for the calibrated and the uncalibrated model with dimensions
$d = 1$ and $d = 10$ for $500$ independently drawn data sets of $n \in \{4, 16, 64, 256, 1024\}$
samples of $(P_X, Y)$. Computation time indicates the minimum time in the $500$ evaluations
on a computer with a 3.6\,GHz processor. The ground truth values of the uncalibrated models were
estimated by averaging the estimates of $\widehat{\mathrm{SKCE}}_{k,1000}$
for $1000$ independently drawn data sets of $1000$ samples of $(P_X, Y)$ (independent from
the data sets used for the evaluation of the estimates). \Cref{fig:synthetic_error_calibrated_1,fig:synthetic_error_calibrated_10} illustrate that
the computational efficiency of $\widehat{\mathrm{SKCE}}_{k,2}$ in comparison with the
other estimators comes at the cost of increased error and variance for the calibrated models
for fixed numbers of samples.

\begin{figure}[hpt]
    \begin{center}
        \includegraphics[scale=0.35]{figures/synthetic/errors_model=calibratedmodel_d=1.pdf}
        \caption{Mean absolute error and variance of 500 calibration error estimates for
        data sets of $n \in \{4, 16, 64, 256, 1024\}$ samples from the calibrated model
        of dimension $d = 1$.}
        \label{fig:synthetic_error_calibrated_1}
    \end{center}
\end{figure}

\begin{figure}[hpt]
    \begin{center}
        \includegraphics[scale=0.35]{figures/synthetic/errors_model=calibratedmodel_d=10.pdf}
        \caption{Mean absolute error and variance of 500 calibration error estimates for
        data sets of $n \in \{4, 16, 64, 256, 1024\}$ samples from the calibrated model
        of dimension $d = 10$.}
        \label{fig:synthetic_error_calibrated_10}
    \end{center}
\end{figure}

\begin{figure}[hpt]
    \begin{center}
        \includegraphics[scale=0.35]{figures/synthetic/errors_model=uncalibratedmodel_d=1.pdf}
        \caption{Mean absolute error and variance of 500 calibration error estimates for
        data sets of $n \in \{4, 16, 64, 256, 1024\}$ samples from the uncalibrated model
        of dimension $d = 1$.}
        \label{fig:synthetic_error_uncalibrated_1}
    \end{center}
\end{figure}

\begin{figure}[hpt]
    \begin{center}
        \includegraphics[scale=0.35]{figures/synthetic/errors_model=uncalibratedmodel_d=10.pdf}
        \caption{Mean absolute error and variance of 500 calibration error estimates for
        data sets of $n \in \{4, 16, 64, 256, 1024\}$ samples from the uncalibrated model
        of dimension $d = 10$.}
        \label{fig:synthetic_error_uncalibrated_10}
    \end{center}
\end{figure}

@@

\begin{figure}[hpt]
    \begin{center}
        \includegraphics[scale=0.35]{figures/synthetic/tests_d=1.pdf}
        \caption{Empirical test errors for 500 data sets of $n \in \{4, 16, 64, 256, 1024\}$
        samples from models with targets of dimension $d = 1$. The dashed black line
        indicates the set signficance level $\alpha = 0.05$.}
        \label{fig:synthetic_tests_1}
    \end{center}
\end{figure}

\begin{figure}[hpt]
    \begin{center}
        \includegraphics[scale=0.35]{figures/synthetic/tests_d=10.pdf}
        \caption{Empirical test errors for 500 data sets of $n \in \{4, 16, 64, 256, 1024\}$
        samples from models with targets of dimension $d = 10$. The dashed black line
        indicates the set signficance level $\alpha = 0.05$.}
        \label{fig:synthetic_tests_10}
    \end{center}
\end{figure}

@@

We train 10 models with different initializations of parameters $\theta$. The initial values
of the weight matrices of the neural networks are sampled from the uniform Glorot
initialization~\citep{Glorot2010} and the offset vectors are initialized with zeros.
In \cref{fig:friedman1}, we visualize estimates of accuracy and calibration measures
on the training and test data set with 100 and 50 samples, respectively, for
5000 training iterations. The pinball loss is a common measure and
training objective for calibration of quantiles~\citep{Song2019}. It is defined
as
\begin{equation*}
    \Exp_{X,Y} L_{\tau}\big(Y, \mathrm{quantile}(P_X, \tau)\big),
\end{equation*}
where $L_{\tau}(y, \tilde{y}) = (1 - \tau) (\tilde{y} - y)_{+} + \tau (y - \tilde{y})_{+}$
and $\mathrm{quantile}(P_x, \tau) = \inf_{y} \{P_x(Y \leq y) \geq \tau\}$ for
quantile level $\tau \in [0, 1]$.
In \cref{fig:friedman1} we plot the average pinball loss (pinball) for
quantile levels $\tau \in \{0.05, 0.1, \ldots, 0.95\}$. Estimates of the $\mathrm{SKCE}_{k,n}$
(SKCE (unbiased)) and $\mathrm{SKCE}_{k}$ (SKCE (biased)) are evaluated for the tensor product kernel
\begin{equation*}
    \begin{split}
        k\big((p, y), (p', y')\big) &= \exp{\big(-W_2(p, p')\big)} \exp{\big(-(y - y')^2 \big)} \\
        &= \exp{\big(-\sqrt{(m_p - m_{p'})^2 - (\sigma_p - \sigma_{p'})^2}\big)} \exp{\big(- (y - y')^2\big)},
    \end{split}
\end{equation*}
where $W_2$ is the 2-Wasserstein distance and $m_p, m_{p'}$ and $\sigma_p, \sigma_{p'}$ denote
the mean and the standard deviation of the normal distributions $p$ and $p'$ (see~\cref{app:normal}).
The $p$-value estimate ($p$-value) is computed by estimating the quantile of the asymptotic distribution
of $n \widehat{\mathrm{SKCE}}_{k,n}$ with 1000 bootstrap samples
(see~\cref{remark:skceb_quadratic}). The estimates of the mean squared error
and the average negative log-likelihood are denoted by MSE and NLL.
All estimators indicate consistently that the trained models suffer from overfitting
after around 1000 training iterations.

Additionally, we form ensemble models of the ten individual models at every training
iteration. The evaluations for the ensembles is visualized in \cref{fig:friedman1} as
well. Apart from the unbiased estimates of $\mathrm{SKCE}_k$, the estimates of the
ensemble models are consistently better than the average estimates of the ensemble
members. For the mean squared error and the negative log-likelihood this behaviour
is guaranteed theoretically by the generalized mean inequality.

\begin{figure}[htp]
    \begin{center}
        \includegraphics[scale=0.07]{figures/friedman/statsplot.png}
        \caption{Estimates of different accuracy and calibration measures of ten
        Gaussian predictive models for the Friedman~1 regression problem versus
        the number of training iterations.
        Evaluations on the training data set (100 samples) and the test data set
        (50 samples) are displayed in green and orange, respectively. The solid line
        and its surrounding band represent the mean and the range of the 10\% to 90\%
        quantile of the evaluations of the ten models. The dashed line visualizes the
        evaluations of the ensemble models.}
        \label{fig:friedman1}
    \end{center}
\end{figure}

@@

Let $P_x = \mathcal{N}(\mu_x, \Sigma_x) \in \mathcal{P}$,
$y \in \mathcal{Y} = \mathbb{R}^d$, and $\gamma > 0$. We obtain
\begin{multline*}
    \Exp_{Z_x \sim P_x} \exp{\Big(- \gamma {\|Z_x - y\|}^2_2\Big)} \\
    = {\big|\mathbf{I}_{d} + 2\gamma \Sigma_x \big|}^{-1/2} \exp{\Big(-\gamma {(\mu_x - y)}^{\mathsf{T}} {\big(\mathbf{I}_d + 2\gamma \Sigma_x
    \big)}^{-1} {(\mu_x - y)}\Big)}
\end{multline*}
from \citet[Theorem~3.2.a3]{mathai1992}. In particular, if
$\Sigma_x = \mathrm{diag}{\Sigma_{x,1}, \ldots, \Sigma_{x,d})}$, then
\begin{multline*}
    \Exp_{Z_x \sim P_x} \exp{\Big(- \gamma {\|Z_x - y\|}^2_2\Big)} \\
    = \prod_{i=1}^{d} \bigg[{\big(1 + 2\gamma \Sigma_{x,i}\big)}^{-1/2} \exp{\Big(-\gamma {\big(1 + 2\gamma \Sigma_{x,i}\big)}^{-1} {\big(\mu_{x,i} - y_i\big)}^2 \Big)}\bigg].
\end{multline*}

>>>>

\begin{figure}[!htb]
    \centering
    \begin{subfigure}[t]{0.62\textwidth}
        \centering
        \textbf{a}
        \includegraphics[valign=t,scale=0.23]{figures/ols/heatmap.pdf}
    \end{subfigure}%
    \hfill%
    \begin{subfigure}[t]{0.38\textwidth}
        \centering
        \textbf{b}
        \includegraphics[valign=t,scale=0.23]{figures/ols/quantiles.pdf}
    \end{subfigure}
    \caption{Illustration of a conditional distribution $\Prob(Y|X)$ with scalar
    feature and target. We consider a Gaussian predictive model $P$, obtained by
    ordinary least squares regression with 100 training data points (orange dots).
    Empirically the predicted quantiles on 50 validation data points appear close
    to being calibrated, although model $P$ is uncalibrated according to
    \cref{def:calibration}. Using the framework in this
    paper, on the same validation data a statistical test allows us to reject
    the null hypothesis that model $P$ is calibrated at a significance level of
    $\alpha = 0.05$ ($p < 0.05$). See~\cref{app:ols} for details.}%
    \label{fig:ols_motivation}
    %\vspace{-0.5\baselineskip}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[scale=0.35]{figures/synthetic/tests_dim=10.pdf}
    \caption{Empirical test errors for 500 data sets of $n \in \{4, 16, 64, 256, 1024\}$
    samples from models with targets of dimension $d = 10$. The dashed black line
    indicates the set signficance level $\alpha = 0.05$.}%
    \label{fig:synthetic_tests_10_main}
    \vspace{-\baselineskip}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[scale=0.35]{figures/friedman/statsplot_zoom.pdf}
    \caption{Mean squared error (MSE), average negative log-likelihood (NLL),
    $\widehat{\mathrm{SKCE}}_k$ (SKCE (biased)), and $p$-value approximation ($p$-value) of
    ten Gaussian predictive models for the Friedman~1 regression problem versus
    the number of training iterations.
    Evaluations on the training data set (100 samples) are displayed in green
    and orange, and on the test data set (50 samples) in blue and purple.
    The green and blue line and their surrounding bands represent
    the mean and the range of the evaluations of the ten models. The orange and
    purple lines visualize the evaluations of the ensemble models.}%
    \label{fig:friedman1_zoom}
    \vspace{-\baselineskip}
\end{figure}

@@

A validation data set of $n = 50$ i.i.d.\ pairs of $X$ and $Y$ is used to
evaluate the empirical cumulative probability
\begin{equation*}
    n^{-1} \sum_{i=1}^n \mathbbm{1}_{[0,\tau]}\big(P(Y \leq Y_i | X = X_i)\big)
\end{equation*}
of model $P$ for quantile levels $\tau \in [0, 1]$. Model $P$ would be quantile
calibrated~\citep{Song2019}
\begin{equation*}
    \tau = \Prob_{X',Y'}\big(P(Y \leq Y' | X = X') \leq \tau \big)
\end{equation*}
for all $\tau \in [0,1]$, where $(X, Y)$ and $(X', Y')$ are independent identically
distributed pairs of random variables (see~\cref{fig:ols_quantiles}).

\begin{figure}[hpt]
    \begin{center}
        \includegraphics[scale=0.35]{figures/ols/quantiles.pdf}
        \caption{Cumulative probability versus quantile level for the linear regression
        model on the validation data (orange curve). The green curve indicates the theoretical ideal
        for a quantile-calibrated model.}
        \label{fig:ols_quantiles}
    \end{center}
\end{figure}

Additionally, we compute a $p$-value estimate of the null hypothesis $H_0$ that model $P$
is calibrated using an estimation of the quantile of the asymptotic distribution
of $n \widehat{\mathrm{SKCE}}_{k,n}$ with 100000 bootstrap samples
on the validation data set (see~\cref{remark:skceb_quadratic}). Kernel $k$ is chosen
as a tensor product kernel of two Gaussian kernels
\begin{equation*}
    \begin{split}
        k\big((p, y), (p', y')\big) &= \exp{\big(-W_2(p, p')\big)} \exp{\big(-(y - y')^2/2 \big)} \\
        &= \exp{\bigg(-\sqrt{(m_p - m_{p'})^2 - (\sigma_p - \sigma_{p'})^2}\bigg)} \exp{\big(- (y - y')^2/2\big)},
    \end{split}
\end{equation*}
where $W_2$ is the 2-Wasserstein distance and $m_p, m_{p'}$ and $\sigma_p, \sigma_{p'}$ denote
the mean and the standard deviation of the normal distributions $p$ and $p'$ (see~\cref{app:normal}).
We obtain $p < 0.05$ in our experiment, and hence the calibration test rejects $H_0$ at the
significance level $\alpha = 0.05$.

@@

We perform an evaluation of the convergence and computation time of the biased estimator
$\widehat{\mathrm{SKCE}}_k$ and the unbiased estimator $\widehat{\mathrm{SKCE}}_{k,B}$ with
blocks of size $B \in \{2, \sqrt{n}, n\}$. We use a tensor product kernel
\begin{equation*}
\begin{split}
    k\big((p, y), (p', y')\big) &= \exp{\big(- W_2(p, p')\big)} \exp{\big(-(y - y')^2/2\big)} \\
    &= \exp{\bigg(-\sqrt{(m_p - m_{p'})^2 - (\sigma_p - \sigma_{p'})^2}\bigg)} \exp{\big( - (y - y')^2/2\big)},
\end{split}
\end{equation*}
where $W_2$ is the 2-Wasserstein distance and $m_p, m_{p'}$ and $\sigma_p, \sigma_{p'}$
denote the mean and the standard deviation of the normal distributions $p$ and $p'$.

\Cref{fig:synthetic_estimators_calibrated_1,fig:synthetic_estimators_calibrated_10,fig:synthetic_estimators_uncalibrated_1,fig:synthetic_estimators_uncalibrated_10} visualize the mean absolute error and the variance
of the resulting estimates for the calibrated and the uncalibrated model with dimensions
$d = 1$ and $d = 10$ for $500$ independently drawn data sets of $n \in \{4, 16, 64, 256, 1024\}$
samples of $(P_X, Y)$. Computation time indicates the minimum time in the $500$ evaluations
on a computer with a 3.6\,GHz processor. The ground truth values of the uncalibrated models were
estimated by averaging the estimates of $\widehat{\mathrm{SKCE}}_{k,1000}$
for $1000$ independently drawn data sets of $1000$ samples of $(P_X, Y)$ (independent from
the data sets used for the evaluation of the estimates). \Cref{fig:synthetic_estimators_calibrated_1,fig:synthetic_estimators_calibrated_10} illustrate that
the computational efficiency of $\widehat{\mathrm{SKCE}}_{k,2}$ in comparison with the
other estimators comes at the cost of increased error and variance for the calibrated models
for fixed numbers of samples.

\begin{figure}[hpt]
    \begin{center}
        \includegraphics[scale=0.35]{figures/synthetic/estimators_calibrated_model_dim=1.pdf}
        \caption{Mean absolute error and variance of 500 calibration error estimates for
        data sets of $n \in \{4, 16, 64, 256, 1024\}$ samples from the calibrated model
        of dimension $d = 1$.}
        \label{fig:synthetic_estimators_calibrated_1}
    \end{center}
\end{figure}

\begin{figure}[hpt]
    \begin{center}
        \includegraphics[scale=0.35]{figures/synthetic/estimators_calibrated_model_dim=10.pdf}
        \caption{Mean absolute error and variance of 500 calibration error estimates for
        data sets of $n \in \{4, 16, 64, 256, 1024\}$ samples from the calibrated model
        of dimension $d = 10$.}
        \label{fig:synthetic_estimators_calibrated_10}
    \end{center}
\end{figure}

\begin{figure}[hpt]
    \begin{center}
        \includegraphics[scale=0.35]{figures/synthetic/estimators_uncalibrated_model_dim=1.pdf}
        \caption{Mean absolute error and variance of 500 calibration error estimates for
        data sets of $n \in \{4, 16, 64, 256, 1024\}$ samples from the uncalibrated model
        of dimension $d = 1$.}
        \label{fig:synthetic_estimators_uncalibrated_1}
    \end{center}
\end{figure}

\begin{figure}[hpt]
    \begin{center}
        \includegraphics[scale=0.35]{figures/synthetic/estimators_uncalibrated_model_dim=10.pdf}
        \caption{Mean absolute error and variance of 500 calibration error estimates for
        data sets of $n \in \{4, 16, 64, 256, 1024\}$ samples from the uncalibrated model
        of dimension $d = 10$.}
        \label{fig:synthetic_estimators_uncalibrated_10}
    \end{center}
\end{figure}

@@

\begin{figure}[hpt]
    \begin{center}
        \includegraphics[scale=0.35]{figures/synthetic/tests_dim=1.pdf}
        \caption{Empirical test errors for 500 data sets of $n \in \{4, 16, 64, 256, 1024\}$
        samples from models with targets of dimension $d = 1$. The dashed black line
        indicates the set signficance level $\alpha = 0.05$.}
        \label{fig:synthetic_tests_1}
    \end{center}
\end{figure}

\begin{figure}[hpt]
    \begin{center}
        \includegraphics[scale=0.35]{figures/synthetic/tests_dim=10.pdf}
        \caption{Empirical test errors for 500 data sets of $n \in \{4, 16, 64, 256, 1024\}$
        samples from models with targets of dimension $d = 10$. The dashed black line
        indicates the set signficance level $\alpha = 0.05$.}
        \label{fig:synthetic_tests_10}
    \end{center}
\end{figure}

@@

We train 10 models with different initializations of parameters $\theta$. The initial values
of the weight matrices of the neural networks are sampled from the uniform Glorot
initialization~\citep{Glorot2010} and the offset vectors are initialized with zeros.
In \cref{fig:friedman1}, we visualize estimates of accuracy and calibration measures
on the training and test data set with 100 and 50 samples, respectively, for
5000 training iterations. The pinball loss is a common measure and
training objective for calibration of quantiles~\citep{Song2019}. It is defined
as
\begin{equation*}
    \Exp_{X,Y} L_{\tau}\big(Y, \mathrm{quantile}(P_X, \tau)\big),
\end{equation*}
where $L_{\tau}(y, \tilde{y}) = (1 - \tau) (\tilde{y} - y)_{+} + \tau (y - \tilde{y})_{+}$
and $\mathrm{quantile}(P_x, \tau) = \inf_{y} \{P_x(Y \leq y) \geq \tau\}$ for
quantile level $\tau \in [0, 1]$.
In \cref{fig:friedman1} we plot the average pinball loss (pinball) for
quantile levels $\tau \in \{0.05, 0.1, \ldots, 0.95\}$. Estimates of the $\mathrm{SKCE}_{k,n}$
(SKCE (unbiased)) and $\mathrm{SKCE}_{k}$ (SKCE (biased)) are evaluated for the tensor product kernel
\begin{equation*}
    \begin{split}
        k\big((p, y), (p', y')\big) &= \exp{\big(-W_2(p, p')\big)} \exp{\big(-(y - y')^2/2 \big)} \\
        &= \exp{\bigg(-\sqrt{(m_p - m_{p'})^2 - (\sigma_p - \sigma_{p'})^2}\bigg)} \exp{\big(- (y - y')^2/2\big)},
    \end{split}
\end{equation*}
where $W_2$ is the 2-Wasserstein distance and $m_p, m_{p'}$ and $\sigma_p, \sigma_{p'}$ denote
the mean and the standard deviation of the normal distributions $p$ and $p'$ (see~\cref{app:normal}).
The $p$-value estimate ($p$-value) is computed by estimating the quantile of the asymptotic distribution
of $n \widehat{\mathrm{SKCE}}_{k,n}$ with 1000 bootstrap samples
(see~\cref{remark:skceb_quadratic}). The estimates of the mean squared error
and the average negative log-likelihood are denoted by MSE and NLL.
All estimators indicate consistently that the trained models suffer from overfitting
after around 1000 training iterations.

Additionally, we form ensemble models of the ten individual models at every training
iteration. The evaluations for the ensembles are visualized in \cref{fig:friedman1} as
well. Apart from the unbiased estimates of $\mathrm{SKCE}_k$, the estimates of the
ensemble models are consistently better than the average estimates of the ensemble
members. For the mean squared error and the negative log-likelihood this behaviour
is guaranteed theoretically by the generalized mean inequality.

\begin{figure}[htp]
    \begin{center}
        \includegraphics[scale=0.35]{figures/friedman/statsplot.pdf}
        \caption{Estimates of different accuracy and calibration measures of ten
        Gaussian predictive models for the Friedman~1 regression problem versus
        the number of training iterations.
        Evaluations on the training data set (100 samples) are displayed in green
        and orange, and on the test data set (50 samples) in blue and purple.
        The green and blue line and their surrounding bands represent
        the mean and the range of the evaluations of the ten models. The orange and
        purple lines visualize the evaluations of the ensemble models.}
        \label{fig:friedman1}
    \end{center}
\end{figure}

@@

Let $P_x = \mathcal{N}(\mu_x, \Sigma_x) \in \mathcal{P}$,
$y \in \mathcal{Y} = \mathbb{R}^d$, and $\gamma > 0$. We obtain
\begin{multline*}
    \Exp_{Z_x \sim P_x} \exp{\Big(- \gamma {\|Z_x - y\|}^2_2\Big)} \\
    = {\big|\mathbf{I}_{d} + 2\gamma \Sigma_x \big|}^{-1/2} \exp{\Big(-\gamma {(\mu_x - y)}^{\mathsf{T}} {\big(\mathbf{I}_d + 2\gamma \Sigma_x
    \big)}^{-1} {(\mu_x - y)}\Big)}
\end{multline*}
from \citet[Theorem~3.2.a3]{mathai1992}. In particular, if
$\Sigma_x = \mathrm{diag}{(\Sigma_{x,1}, \ldots, \Sigma_{x,d})}$, then
\begin{multline*}
    \Exp_{Z_x \sim P_x} \exp{\Big(- \gamma {\|Z_x - y\|}^2_2\Big)} \\
    = \prod_{i=1}^{d} \bigg[{\big(1 + 2\gamma \Sigma_{x,i}\big)}^{-1/2} \exp{\Big(-\gamma {\big(1 + 2\gamma \Sigma_{x,i}\big)}^{-1} {\big(\mu_{x,i} - y_i\big)}^2 \Big)}\bigg].
\end{multline*}
